Optimal (Multiway) Spatial Joins

### 2024-05-29 msj.tex
yufei

\noindent \underline{\em Proof of Statement (2).} Fix any rectangle $r \in R_1 \cup ... \cup R_{k-2}$ and any horizontal segment $h = [x_1, x_2] \times y$ from $H$ that crosses $r$. We will show that $h$ must also cross the trimmed rectangle $r'$ of $r$. From the fact of $h$ crossing $r$, it is clear that $[x_1, x_2]$ contains the x-range of $r$. As the x-range of $r$ contains that of $r'$, we can assert that $[x_1, x_2]$ contains the x-range of $r'$. To prove that $h$ crosses $r'$, we still need to show $y \in [\ybot(r'), \ytop(r')]$. Recall that $\ybot(r')$ is the y-coordinate of the lowest segment in $H$ crossing $r$. This implies $y \ge \ybot(r')$ because $h$ itself is a segment in $H$ crossing $r$. Analogously, it also holds that $y \le \ytop(r')$. We can now conclude that $h$ crosses $r'$.

@@

Fix any rectangle $r \in R_1 \cup ... \cup R_{k-2}$ and any vertical segment $v$ from $V$ that crosses $r$. An argument symmetric to the above shows that $v \in V$ must also cross $r'$.

@@

We now prove the first bullet of statement (2), namely, $\bm{t}\in \J(R_1',...,R_{k-2}')$. Consider the $k$-tuple $(r_1,...,r_{k-2},h,v)\in \J_1$ given in statement (2). By definition of $\J_1$, segments $h$ and $v$ both cross each of the rectangles $r_1,..., r_{k-2}$. By the earlier discussion, $h$ and $v$ must also cross each of the trimmed rectangles $r_1',..., r_{k-2}'$. Hence, the intersection of $h$ and $v$ must be a point covered by each of $r_1',..., r_{k-2}'$, suggesting the point is in $\bigcap_{i = 1}^{k-2}r_i'$, which is thus not empty. Therefore, $\bm{t} = (r_1', ..., r_{k-2}')$ is a result tuple in $\J(R_1',...,R_{k-2}')$.

@@

Next, we prove the second bullet, namely, $h \in \dcross_H(\bm{t})$ and $v \in \dcross_H(\bm{t})$. It suffices to show only the former due to symmetry. To prove $h \in \dcross_H(\bm{t})$, we need to argue that $h$ crosses $\gbot(\bm{t})$ and $B_\bm{t}$. The first part, $h$ crossing $\gbot(\bm{t})$, is done because, as already explained, $h$ crosses each of $r_1', ..., r_{k-2}'$, and $\gbot(\bm{t})$ is one of those $k-2$ rectangles. To prove that $h$ crosses $B_\bm{t}$, first note that $B_\bm{t}$ (which is the intersection of $r_1', ..., r_{k-2}'$) is covered by $\gbot(\bm{t})$. From the fact that $h$ crosses $\gbot(\bm{t})$, we can assert that the y-range of $h$ contains that of $B_\bm{t}$. Hence, either $h$ is disjoint with $B_\bm{t}$ or $h$ crosses $B_\bm{t}$. However, $h$ cannot be disjoint with $B_\bm{t}$ because, as shown earlier, the intersection of $h$ and $v$ falls in $B_\bm{t}$. It thus follows that $h$ crosses $B_\bm{t}$.

>>>>

\noindent \underline{\em Proof of Statement (2).} Fix any rectangle $r \in R_1 \cup ... \cup R_{k-2}$ and any horizontal segment $h = [x_1, x_2] \times y$ from $H$ that crosses $r$. We will show that $h$ must also cross the trimmed rectangle $r'$ of $r$. From the fact of $h$ crossing $r$, it is clear that $[x_1, x_2]$ contains the x-range of $r$. As the x-range of $r$ contains that of $r'$, we can assert that $[x_1, x_2]$ contains the x-range of $r'$. To prove that $h$ crosses $r'$, we still need to show $y \in [\ybot(r'), \ytop(r')]$. Recall that $\ybot(r')$ is the y-coordinate of the lowest segment in $H$ crossing $r$. This implies $y \ge \ybot(r')$ because $h$ itself is a segment in $H$ crossing $r$. Analogously, it also holds that $y \le \ytop(r')$. We can thus conclude that $h$ crosses $r'$.

@@

Fix any rectangle $r \in R_1 \cup ... \cup R_{k-2}$ and any vertical segment $v$ from $V$ that crosses $r$. An argument symmetric to the above shows that $v$ must also cross $r'$.

@@

We now prove the first bullet of statement (2), namely, $\bm{t}\in \J(R_1',...,R_{k-2}')$. Consider the $k$-tuple $(r_1,...,r_{k-2},h,v)\in \J_1$ given in statement (2). By definition of $\J_1$, segments $h$ and $v$ both cross each of the rectangles $r_1,..., r_{k-2}$. By the earlier discussion, $h$ and $v$ must also cross each of the trimmed rectangles $r_1',..., r_{k-2}'$. Hence, the intersection of $h$ and $v$ must be a point covered by each of $r_1',..., r_{k-2}'$. This suggests that the point is in $\bigcap_{i = 1}^{k-2}r_i'$, which thus cannot be empty. Therefore, $\bm{t} = (r_1', ..., r_{k-2}')$ is a result tuple in $\J(R_1',...,R_{k-2}')$.

@@

Next, we prove the second bullet, namely, $h \in \dcross_H(\bm{t})$ and $v \in \dcross_H(\bm{t})$. It suffices to show only the former due to symmetry. To prove $h \in \dcross_H(\bm{t})$, we need to argue that $h$ crosses $\gbot(\bm{t})$ and $B_\bm{t}$. The first part, $h$ crossing $\gbot(\bm{t})$, is done because, as already explained, $h$ crosses each of $r_1', ..., r_{k-2}'$, and $\gbot(\bm{t})$ is one of those $k-2$ rectangles. To prove that $h$ crosses $B_\bm{t}$, first note that $B_\bm{t}$ (which is the intersection of $r_1', ..., r_{k-2}'$) is covered by $\gbot(\bm{t})$. The fact that $h$ crosses $\gbot(\bm{t})$ indicates that the y-range of $h$ contains that of $B_\bm{t}$. Hence, either $h$ is disjoint with $B_\bm{t}$ or $h$ crosses $B_\bm{t}$. However, $h$ cannot be disjoint with $B_\bm{t}$ because, as shown earlier, the intersection of $h$ and $v$ falls in $B_\bm{t}$. It thus follows that $h$ crosses $B_\bm{t}$.
